---
output: github_document
bibliography: vignettes/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# MGPMSimulations

The package MGPMSimulations contains all scripts and simulated data that have been created or generated for the simulation-based study in the research article [@Mitov:2019a] (see References).

## Installation

The easiest way to install this package is to use the function `install_github()` from the R-package devtools. The following command will install the most up-to-date version of the master branch from the github repository of the package. 

```{r, eval=FALSE}
devtools::install_github("venelin/MGPMSimulations")
```

## License 

The package MGPMSimulations is distributed under the terms of the 
[Creative Commons Attribution 4.0 International License (CC BY 4.0)](https://creativecommons.org/licenses/by/4.0/legalcode) license. 

## Citing MGPMSimulations
Please, read the following:
```{r}
print(citation("MGPMSimulations"), bibtex = TRUE)
```

## Further information
For additional information about the data objects and scripts in the package, read [SI Appendix, Sections I,J,L.2 and L.3](https://www.pnas.org/lookup/suppl/doi:10.1073/pnas.1813823116/-/DCSupplemental) from [@Mitov:2019a].

# References

